On the adhesivity of EGGS

### 2025-02-19 calco/eggs.tex
eggs
minori
minima

\begin{proof}
	Let $\mathcal{P} = (A, B, C, s, t, q)$, $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i^\star \circ s_i$, and let $(U, u_1, u_2)$ the kernel pair of $q^\star \circ s$ .
	Consider then the following situation.
	\[\xymatrix@C=10pt@R=6pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar[dl]_{k_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){k_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{C_1^\star}\ar[rr]|\hole^(.65){h_C^\star}\ar[dl]^{m_C^\star} && {C_2^\star} \ar[dl]^{n_C^\star} \\{C_3^\star} \ar[rr]_{k_C^\star} & & C}\]
	Since $m$ is regular mono, $m_C$ is mono ({\color{red}{inserire citazione}}). Then, by adhesivity of $\Set$, the bottom face is a Van Kampen square, hence a pushout. Therefore, by ({\color{red}{citazione}}), the square below is a pushout.
	\[\xymatrix{K_1\ar[r]^{f_k}\ar[d]_{f_m}&K_2\ar[d]^{f_n}\\K_3\ar[r]_{f_k}&U}\]
\end{proof}

>>>>

\begin{proof}
	Let $\mathcal{P} = (A, B, C, s, t, q)$, $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i^\star \circ s_i$, and let $(U, u_1, u_2)$ the kernel pair of $q^\star \circ s$ .
	Consider then the following situation.
	\[\xymatrix@C=10pt@R=6pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar[dl]_{k_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){k_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{C_1^\star}\ar[rr]|\hole^(.65){h_C^\star}\ar[dl]^{m_C^\star} && {C_2^\star} \ar[dl]^{n_C^\star} \\{C_3^\star} \ar[rr]_{k_C^\star} & & C}\]
	Since $m$ is regular mono, $m_C$ is mono ({\color{red}{inserire citazione}}). Then, by adhesivity of $\Set$, the bottom face is a Van Kampen square, hence a pushout. Therefore, by \Cref{lem:mpo} , the square below is a pushout.
	\[\xymatrix{K_1\ar[r]^{f_k}\ar[d]_{f_m}&K_2\ar[d]^{f_n}\\K_3\ar[r]_{f_k}&U}\]
       Computing, we have
        \[
                \begin{split}
                        q^\star \circ t \circ u_1 \circ f_n &= q^\star \circ t \circ n_E \circ \pi_2^1 \\ &= n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^1 \\&= n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^2 \\&=q^\star \circ t \circ u_2 \circ f_n 
                        \end{split}
                        \qquad
                        \begin{split} q^\star \circ t \circ u_1 \circ f_k &= q^\star \circ t \circ k_E \circ \pi_3^1 \\ &= k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^1 \\&= k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^2 \\&=q^\star \circ t \circ u_2 \circ f_k
                        \end{split}
        \]
        By universal property of pushouts, we deduce $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the thesis follows.
\end{proof}

By direct application of \Cref{thm:slice-functors}, we can conclude what follows.

\begin{corollary}
	$\egg$ is $\reg(\egg)$-adhesive.
\end{corollary}
